### 2024-10-30 main_widom_morse.tex
fixed diacritics in bib-file, tex-file: some corrections in text, add terminating P*, add keywords in eng (commented), add abstract and keywords in ukr (commented), add bibliography in UJP style after end-document

@@

 In the supercritical region, substances no longer behave distinctly as either liquids or gases but exist as a single, continuous phase without a sharp liquid-gas boundary. However, fluids can still exhibit liquid-like and gas-like behaviors beyond the critical temperature. A way to represent a conditional boundary between these regions in supercritical fluids is the Widom line \--- a continuation of the coexistence line based on the locus of maxima of certain thermodynamic response functions~\cite{XKBetal05,MS10,SBGetal10}. This occurs because near CP, the system experiences significant fluctuations in density over increasingly large spatial scales. Although, the equation of state~\eqref{eq:eosPTM_reduced} is derived in the mean-field-like approximation, we established in~\cite{DKRP24arxiv,DKRP24} that the isothermal compressibility of the cell fluid model diverges at CP and consequently displays maxima in the supercritical region (see Figures~\ref{fig3}). This suggests the possibility of deriving the Widom line and expanding the phase diagram in Figure~\ref{fig2} beyond CP.
 In what follows we consider this in more detail.

@@

Below the critical temperature, negative values of $M$ correspond to gaseous densities, while positive values of $M$ represent liquid densities. Above the critical point, the fluid becomes continuous. However, Figure~\ref{fig3} clearly shows significantly higher isothermal compressibility in the region where $M<0$, near the base of the maxima ridge, compared to the compressibility values in the $M>0$ region. In the first case ($M<0$), the supercritical fluid exhibits gas-like behavior. In the second case ($M>0$), it behaves like a liquid. Far beyond the critical point ($\tau > 0.5$), there is no noticeable difference in $\kappa_T$ values around the effective chemical potential $M=0$. At $\tau = 0.2$ the compressibility maxima become almost undistinguished, they completely vanish at $\tau > 0.28$. 

@@

	\caption{The reduced thermal expansion $\alpha^*_P$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$. The plot focuses on a range of $M$ around its critical value $0$, thin dashed black line displays maxima locus of $\alpha^*_T$.

@@

Similarly to the isothermal compressibility, similar arguments apply to the thermal expansion coefficient defined as
\begin{equation}
	\alpha_{P} = \frac{1}{V} \left(\frac{\partial V}{\partial T}\right)_{P,N}.
\end{equation}
Its reduced counterpart is calculated based on EoS~\eqref{eq:eosMT} by formula
\begin{eqnarray}
	\alpha^*_P & = & \frac{1}{T^*_c \rho^*}
	\left[ 
	-\left(\frac{\partial \rho^*}{\partial \tau}\right)_{\mu}
	\right. \nonumber\\
	&& + \left.\left(\frac{\partial \rho^*}{\partial \mu}\right)_{T}
	\left(\frac{\partial P^*}{\partial \tau}\right)_{\mu}
	\left(\frac{\partial P^*}{\partial \mu}\right)^{-1}_{T} 
	\right].
\end{eqnarray}
Figure~\ref{fig3b} illustrates the dependence of $\alpha^*_{P}$ on $M$ at some given values of $\tau$, at $T>T_c$. The thermal expansion coefficient also develops a ridge of maxima in the supercritical phase, that vanishes at $\tau > 0.35$.
To identify the Widom line based on the locus of the thermal expansion coefficient maxima, we solve the equation
\begin{equation}\label{eq:maximize_alpha}
	\frac{\partial \alpha_P^*}{\partial M} = 0
\end{equation}
with respect to $M$.
Substituting the solution of \eqref{eq:maximize_alpha} into the equation of state \eqref{eq:eosMT}, one locates another Widom line in the pressure-temperature plane (see Figure~\ref{fig4}, dash-dotted line). This is the second option for the separation line between liquid-like and gas-like fluid.

The third choice for the boundary between liquid-like and gas-like regions beyond CP is based on the condition $M=0$. On the one hand, within the present approach, the condition $M=0$ holds along phase coexistence up to the critical point. Thus, the implementation of the condition  $M=0$ above CP seems to be a natural continuation of the coexistence line into the supercritical region. On the other hand, taking into account the functional form of the grand partition function~\cite{KD16,KR09}, the condition of $M=0$ is equivalent to the absence of an external field in the Ising model. This analogy is interesting from the perspective of direct mapping between the Ising model and fluids~\cite{Kulinskii10jcp,BK11}. In Fig.~\ref{fig4} the separation line based on this condition $M=0$ is given by the dotted curve.

@@

	%@incollection{KKD2018,
		%  title={Phase Transitions in a Continuum {C}urie-{W}eiss System: A Quantitative Analysis},
		%  author={Kozitsky, Yu. and Kozlovskii, M. and Dobush, O.},
		%  booktitle={Modern Problems of Molecular Physics},
		%  editor={Bulavin, L. A. Chalyi, A. V.},
		%  pages={229--251},
		%  year={2018},
		%  publisher={Springer},
		%  address={Cham, Switzerland}

		\bibitem{KnezEtAl2014} {\v{Z}}. Knez, E. Marko{\v{c}}i{\v{c}}, M. Leitgeb, M. Primo{\v{z}}i{\v{c}}, M. Knez Hrn{\v{c}}i{\v{c}}, M. {\v{S}}kerget, Industrial applications of supercritical fluids: A review, Energy, 77 (2014) 235-243. % https://doi.org/10.1016/j.energy.2014.07.044
		\bibitem{BrykEtAl2017} T. Bryk, F. A. Gorelli, I. Mryglod, G. Ruocco, M. Santoro, T. Scopigno. Behavior of Supercritical Fluids across the “Frenkel Line”. The Journal of Physical Chemistry Letters 2017 8 (20), 4995-5001 %	DOI: 10.1021/acs.jpclett.7b02176
		\bibitem{CampiEtAl2001} Campi, X., Krivine, H., Sator, N. Percolation line of self-bound clusters in supercritical fluids. Physica A: Statistical Mechanics and its Applications, 296(1-2), 24-30 (2001). %https://doi.org/10.1016/S0378-4371(01)00158-3
		\bibitem{XuEtAl2005}Xu, L., Kumar, P., Buldyrev, S. V., Chen, S.-H., Poole, P. H., Sciortino, F., Stanley, H. E. Relation between the Widom line and the dynamic crossover in systems with a liquid-liquid phase transition. Proceedings of the National Academy of Sciences, 102(46), 16558–16562  (2005). doi:10.1073/pnas.0507870102 
		\bibitem{McMillanStanley2010} McMillan, P., Stanley, H. Going supercritical. Nature Phys 6, 479–480 (2010). %https://doi.org/10.1038/nphys1711
		\bibitem{SimeoniEtAl2010} Simeoni, G., Bryk, T., Gorelli, F. et al. The Widom line as the crossover between liquid-like and gas-like behaviour in supercritical fluids. Nature Phys 6, 503–507 (2010). %https://doi.org/10.1038/nphys1683
		\bibitem{ArtemenkoEtAl2017} Artemenko, S., Krijgsman, P., Mazur, V. The Widom line for supercritical fluids. Journal of Molecular Liquids, 238, 122-128 (2017). %http://dx.doi.org/10.1016/j.molliq.2017.03.107
		\bibitem{Proctor2020Book} J.~E. Proctor, The liquid and supercritical fluid states of matter. CRC Press (2020). %[ISBN 9780429491443]

		\bibitem{KozlovskiiDobush2020}  M.P. Kozlovskii and O.A. Dobush,  Ukr. J. Phys. {\bf 65} 428 (2020).
		\bibitem{DobushEtAl2024} O.A. Dobush, M.P. Kozlovskii, R.V. Romanik, I.V. Pylyuk, arXiv preprint 2409.09786 (2024)
		\bibitem{KozlovskiiDobush2016}  M. Kozlovskii and O. Dobush, J. Mol. Liq., {\bf 215}, 58, (2016).

%		\bibitem{refb}  I.V. Pylyuk and O.A. Dobush,  Ukr. J. Phys. {\bf 65} 1080 (2020).
%		\bibitem{refc0} I.V. Pylyuk and M.P. Kozlovskii, O.A. Dobush, M.V. Dufanets, J. Mol. Liq., {\bf 355}, 122322, (2023).
%		\bibitem{refc1} I.V. Pylyuk and M.P. Kozlovskii, O.A. Dobush, Ukr. J. Phys., {\bf 68}, 601, (2023).
%		\bibitem{refc}  M.P. Kozlovskii and O.A. Dobush, Condens. Matter Phys., {\bf 20}, 23501,(2017).
%		\bibitem{refd}  M.P. Kozlovskii and I.V. Pylyuk, O.A. Dobush, Condens. Matter Phys., {\bf 21}, 43502, (2018).
%		\bibitem{ref8}  R.C. Lincoln and K.M. Koliwad, Phys. Rev., {\bf 157}, 463, (1967).
%		\bibitem{ref9}  J.K. Singh, J. Adhikari, and S.K. Kwak, Fluid Phase Equilibria, {\bf 248}, 1, (2006).

%		\bibitem{ref16} M.V.~Fedoryuk, \textit{Asymptotic methods in analysis} in {\it Analysis I: Integral Representations and Asymptotic Methods}, eds. M.A. Evgrafov and R.V. Gamkrelidze  (Encyclopaedia of Mathematical Sciences 13, Springer-Verlag Berlin Heidelberg, 1989) pp.~83--191.

%		\bibitem{ref11} A. J. Schultz and D. A. Kofke, Fluid Phase Equilibria, {\bf 409}, 12, (2016).
%		\bibitem{ref12} A. J. Masters, J. Phys.: Condens. Matter, {\bf 20}, 283102, (2008).
%		\bibitem{ref13} M. V. Ushcats, J. Chem. Phys., {\bf 140}, 234309, (2014).
%		\bibitem{ref14} D. Pini and G. Stell, N. B. Wilding, Mol. Phys., {\bf95}, 483, (1998).
%		\bibitem{ref15} C.-L. Lee and G. Stell, J. Hoye, J. Mol. Liq., {\bf 112}, 13, (2004).
%		\bibitem{ref1}  Y. Kozitsky and M. Kozlovskii, O. Dobush, In \emph{Modern Problems of Molecular Physics}, Springer, 229--251 (2018).
%		\bibitem{ref3}  M.P. Kozlovskii and O.A. Dobush, I.V. Pylyuk, Ukr. J. Phys. {\bf 62} 865 (2017).
%		\bibitem{ref4}  I. Yukhnovskii and V. Kolomiets, I. Idzyk, Condens. Matter Phys., {\bf 16}, 23604, (2013).
%		\bibitem{ref5}  I.R. Yukhnovskii, Condens. Matter Phys., {\bf 17}, 43001, (2014).

%		\bibitem{ref10} I.R. Yukhnovskii and M.P. Kozlovskii, I.V. Pylyuk, Phys. Rev. B, {\bf 66}, 134410, (2002).
%		\bibitem{ref17} D. Pini and G. Stell, N. B. Wilding, Mol. Phys., \textbf{95}, 483, (1998).
%		\bibitem{ref18} J.-M. Caillol, Mol. Phys., {\bf 104}, 1931, (2006).
%		\bibitem{ref19} I.R Yukhnovskii., Theoret. and Math. Phys., \textbf{194}, 224, (2018).
%		\bibitem{ref20} A. Oleinikova and L. Bulavin, V. Pipich, Chem. Phys. Let., {\bf 278}, 121, (1997).
%		\bibitem{ref21} G. Brunner, J. Supercrit. Fluids, {\bf 47}, 373, (2009).
%		\bibitem{ref22} G. Brunner, J. Supercrit. Fluids, {\bf 47}, 382, (2009).

%	\bibitem{ref1} 
%	\bibitem{ref2}
%	\bibitem{ref3}
%	\bibitem{ref4} 
%	\bibitem{ref5}
%	\bibitem{ref6}
%	\bibitem{ref7}
%	\bibitem{ref8}
%	\bibitem{ref9}
%	\bibitem{ref10}
%	\bibitem{ref11}
%	\bibitem{ref12}
%	\bibitem{ref13}
%	\bibitem{ref14}
%	\bibitem{ref15}
%	\bibitem{ref16}
%	\bibitem{ref17}

@@

	The latter expression links the pressure $P$, the temperature $T$ ($\beta = 1/T$ is the inverse temperature), the cell's volume $v$ and the effective chemical potential $M$. In general $M$ is a function of the real chemical potential $\mu$:
\begin{align}
	&	M = \frac{\tilde\mu}{W(0)} + g_1 + n_c \tilde D(0) - \frac{1}{6} \frac{g_3^3}{g_4^2}, \\
	&	\tilde\mu=\mu-\mu^*(1+\tau),
\end{align}
here $\mu^*$ is some positive constant, and $\tau$ is the relative temperature $\tau = (T - T_c) / T_c$,
$T_c$ is the critical temperature. $W(0)$ is what we call an effective interaction potential\footnote{\textbf{explain} what is the effective interaction potential in a few words} at ${\bf k} = 0$:
\begin{equation}
	W(0) = \Phi^{(r)}(0) \left[ B - 1 + \chi_0 + \tau (\chi_0 + A_\gamma) \right].
\end{equation}
Here $\chi_0$ is a constant parameter, the quantities $B$ and $A_\gamma$ reads
\begin{align} 
	& B = 2 \gamma^3 e^{(1-\gamma)/\alpha},\nonumber \\
	& A_\gamma = A e^{(n_0-\gamma)/\alpha} \left( \gamma / n_0\right)^3.
\end{align}
The coefficients $g_n$ are given by the formulas:
\begin{align}
	& g_0 = \ln T_0, \qquad g_1 = T_1/T_0, \qquad g_2 = T_2/T_0 - g_1^2,  \nonumber \\
	& g_3 = T_3/T_0 - g_1^3 - 3g_1 g_2, \quad \qquad  g_4 = T_4/T_0 - g_1^4 - 6 g_1^2 g_2 - 4 g_1 g_3 - 3 g_2^2,
\end{align}
where $T_n(p,\alpha^*)$ are the following special functions
\begin{equation}
	T_n(p,\alpha^*) = \sum_{m=0}^{\infty} \frac{(\alpha^*)^m}{m!} m^n e^{pm^2}.
\end{equation}
Here $\alpha^*=v e^{\beta_c\mu^*}$, and the parameter $p$ has the form
\begin{equation}
	p = \frac{\beta_c}{2} \Phi^{(r)}(0) [\chi_0 + A_\gamma].
\end{equation} 
Note that we denote $\beta_c$ as the inverse critical temperature. Since $p$ fails to be the function of temperature, the coefficients $g_n$ are also temperature-free. The quantity $\tilde D(0)$ which has already appeared in both equations \eqref{eq:eos} and \eqref{3d2} is a function of temperature
\begin{equation}
	\tilde D(0) = g_2 - \frac{1}{2} \frac{g_3^2}{g_4} - \frac{1}{\beta W(0)},
\end{equation}
which equals zero at $T=T_c$. This circumstance gives us an expression for determining the critical temperature 
\begin{equation}
	T_c = \left(g_2 - \frac{1}{2} \frac{g_3^2}{g_4} \right) (B - 1 + \chi_0) \Phi^{(r)}(0).
\end{equation}    
The function $E_\mu(M, T)$ from the equation \eqref{eq:eos} is provided by
\begin{align}
	& E_\mu (M, T) = - \frac{1}{2 N_v} \ln (2\pi \beta W(0)) +  g_0 - \frac{\beta W(0)}{2} \!\! \left( \! \frac{\tilde\mu}{W(0)} \! \right)^{\! 2} \!\!\! - \frac{g_3}{g_4} {M} \! - \frac{g_3^2}{2 g_4^2}  \tilde D(0) - \frac{1}{24} \frac{g_3^4}{g_4^3}. 
\end{align}
Note that for all $ \tau> 0 $ there are no restrictions on the value of $ \bar \rho_0 $, which is a function of the temperature and the chemical potential
\begin{equation}\label{2d18}
	\bar \rho_0 = \left(- \frac{3\bar{M}}{g_4} + \sqrt{Q_t}\right)^{1/3} - \left(  \frac{3\bar{M}}{g_4} + \sqrt{Q_t} \right)^{1/3} \!\!\!\! ,
\end{equation}
where
\begin{equation}
	Q_t = \left(  \frac{2\tilde D(0)}{g_4}\right)^3 + \left( -\frac{3\bar{M}}{g_4}\right)^2, \qquad g_4<0.
\end{equation}  
...
\begin{equation}\label{3d3}
	\bar n = n_g - \bar{M} + \tilde g_2 \gamma_\tau \bar \rho_0,
\end{equation}
where
\begin{equation}\label{3d4}
	n_g = g_1 + n_c \tilde g_2 - \frac{1}{6} g_3^3 / g_4^2.
\end{equation}
...

>>>>

% cell fluid model, Morse potential, supercritical region, Widom line

% Продовжується дослідження коміркової моделі плину з модифікованим потенціалом Морзе. Надкритичні стани розглядаються з огляду на можливість побудови межі розділення між рідиноподібними та газоподібними поведінками. Розраховано три різні лінії, які можна використовувати для цієї мети: лінія максимумів ізотермічної стисливості, лінія максимумів коефіцієнта теплового розширення та лінія, де ефективний хімічний потенціал дорівнює нулю, $M=0$. За симетрією функціоналів статистичних сум умова $M=0$ у рідинах аналогічна відсутності зовнішнього поля в моделі Ізінга. {\textit{К\,л\,ю\,ч\,о\,в\,і\,	с\,л\,о\,в\,а:} коміркова модель, потенціал Морзе, надкритична область, лінія Відома.}

@@

 In the supercritical region, substances no longer behave distinctly as either liquids or gases but exist as a single, continuous phase without a sharp liquid-gas boundary. However, fluids can still exhibit liquid-like and gas-like behaviors beyond the critical temperature. A way to represent a conditional boundary between these regions in supercritical fluids is the Widom line \--- a continuation of the coexistence line based on the locus of maxima of certain thermodynamic response functions~\cite{XKBetal05,MS10,SBGetal10}. This occurs because near CP, the system experiences significant fluctuations in density over increasingly large spatial scales. Although, the equation of state~\eqref{eq:eosMT} is derived in the mean-field-like approximation, we established in~\cite{DKRP24arxiv,DKRP24} that the isothermal compressibility of the cell fluid model diverges at CP and consequently displays maxima in the supercritical region (see Figures~\ref{fig3}). This suggests the possibility of deriving the Widom line and expanding the phase diagram in Figure~\ref{fig2} beyond CP.
 In what follows we consider this in more detail.

@@

Below the critical temperature, negative values of $M$ correspond to gaseous densities, while positive values of $M$ represent liquid densities. Above the critical point, the fluid becomes continuous. However, Figure~\ref{fig3} clearly shows significantly higher isothermal compressibility in the region where $M<0$, near the base of the maxima ridge, compared to the compressibility values in the $M>0$ region. In the first case ($M<0$), the supercritical fluid exhibits gas-like behavior. In the second case ($M>0$), it behaves like a liquid. Far beyond the critical point ($\tau > 0.5$), there is no noticeable difference in $\kappa_T$ values around the effective chemical potential $M=0$. At $\tau = 0.2, P^*>2.30$ the compressibility maxima become almost undistinguished, they completely vanish at $\tau > 0.28$. 

@@

	\caption{The reduced thermal expansion $\alpha^*_P$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$. The plot focuses on a range of $M$ around its critical value $0$, thin dashed black line displays maxima locus of $\alpha^*_P$.

@@

Similarly to the isothermal compressibility, similar arguments apply to the thermal expansion coefficient defined as
\begin{equation}
	\alpha_{P} = \frac{1}{V} \left(\frac{\partial V}{\partial T}\right)_{P,N}.
\end{equation}
Its reduced counterpart is calculated based on EoS~\eqref{eq:eosMT} by formula
\begin{eqnarray}
	\alpha^*_P & = & \frac{1}{T^*_c \rho^*}
	\left[ 
	-\left(\frac{\partial \rho^*}{\partial \tau}\right)_{\mu}
	\right. \nonumber\\
	&& + \left.\left(\frac{\partial \rho^*}{\partial \mu}\right)_{T}
	\left(\frac{\partial P^*}{\partial \tau}\right)_{\mu}
	\left(\frac{\partial P^*}{\partial \mu}\right)^{-1}_{T} 
	\right].
\end{eqnarray}
Figure~\ref{fig3b} illustrates the dependence of $\alpha^*_{P}$ on $M$ at some given values of $\tau$, at $T>T_c$. The thermal expansion coefficient also develops a ridge of maxima in the supercritical phase, that almost vanishes at $\tau > 0.35, P^*>2.75$.
To identify the Widom line based on the locus of the thermal expansion coefficient maxima, we solve the equation
\begin{equation}\label{eq:maximize_alpha}
	\frac{\partial \alpha_P^*}{\partial M} = 0
\end{equation}
with respect to $M$.
Substituting the solution of \eqref{eq:maximize_alpha} into the equation of state \eqref{eq:eosMT}, one locates another Widom line in the pressure-temperature plane (see Figure~\ref{fig4}, dash-dotted line). This is the second option for the separation line between liquid-like and gas-like fluid.

The third choice for the boundary between liquid-like and gas-like regions beyond CP is based on the condition $M=0$. Within the present approach, the condition $M=0$ holds along phase coexistence up to the critical point. Thus, the implementation of the condition $M=0$ above CP seems to be a natural continuation of the coexistence line into the supercritical region. On the other hand, taking into account the functional form of the grand partition function~\cite{KD16,KR09}, the condition of $M=0$ is equivalent to the absence of an external field in the Ising model. This analogy is interesting from the perspective of direct mapping between the Ising model and fluids~\cite{Kulinskii10jcp,BK11}. In Fig.~\ref{fig4} the separation line based on this condition $M=0$ is given by the dotted curve. In the critical region ($\tau<0.02$), beyond CP, the maxima locus of the response functions and the $M=0$ based line visually merge into a single line.

@@

	%1
	\bibitem{KMLetal14} {\v{Z}}.~Knez, E.~Marko{\v{c}}i{\v{c}}, M.~Leitgeb, M.~Primo{\v{z}}i{\v{c}}, M.~Knez Hrn{\v{c}}i{\v{c}}, M.~{\v{S}}kerget.
	\href{https://doi.org/10.1016/j.energy.2014.07.044}{Industrial applications of supercritical fluids: A review}. \textit{Energy} \textbf{77} 235 (2014) [doi: 10.1016/j.energy.2014.07.044]
	%2
	\bibitem{FW69} M.E.~Fisher, B.~Widom.
	\href{https://doi.org/10.1063/1.1671624}{Decay of Correlations in Linear Systems}. \textit{J. Chem. Phys.} \textbf{50} 3756 (1969) [doi: 10.1063/1.1671624]
	%3
	\bibitem{BGMetal17} T.~Bryk, F.A.~Gorelli, I.~Mryglod, G.~Ruocco, M.~Santoro, T.~Scopigno.
	\href{https://doi.org/10.1021/acs.jpclett.7b02176}{Behavior of Supercritical Fluids across the “Frenkel Line”}. \textit{J. Chem. Phys. Lett.} \textbf{8} 4995 (2017) [doi: 10.1021/acs.jpclett.7b02176]
	%4
	\bibitem{CKS01} X.~Campi, H.~Krivine, N.~Sator.
	\href{https://doi.org/10.1016/S0378-4371(01)00158-3}{Percolation line of self-bound clusters in supercritical fluids}. \textit{Physica A} \textbf{296} 24 (2001) [doi: 10.1016/S0378-4371(01)00158-3] 
	%5
	\bibitem{XKBetal05} L.~Xu, P.~Kumar, S.V.~Buldyrev, S.-H.~Chen, P.H.~Poole, F.~Sciortino, H.E.~Stanley.
	\href{https://doi.org/10.1073/pnas.0507870102}{Relation between the Widom line and the dynamic crossover in systems with a liquid-liquid phase transition}. \textit{PNAS} \textbf{102} 16558 (2005) [doi: 10.1073/pnas.0507870102]
	%6
	\bibitem{MS10} P.~McMillan, H.~Stanley.
	\href{https://doi.org/10.1038/nphys1711}{Going supercritical}. \textit{Nature Phys.} \textbf{6} 479 (2010) [doi: 10.1038/nphys1711]
	%7
	\bibitem{AKM17} S.~Artemenko, P.~Krijgsman, V.~Mazur. 
	\href{https://doi.org/10.1016/j.molliq.2017.03.107}{The Widom line for supercritical fluids}. \textit{J. Mol. Liq.} \textbf{238} 122 (2017) [doi: 10.1016/j.molliq.2017.03.107]
	%8
	\bibitem{Proctor20} J.E.~Proctor.
	\href{https://doi.org/10.1201/9780429491443}{The liquid and supercritical fluid states of matter}. (CRC Press, 2020)  [ISBN: 9780429491443]
	%9
	\bibitem{KD20} M.~Kozlovskii, O.~Dobush.
	\href{https://ujp.bitp.kiev.ua/index.php/ujp/article/view/2019631}{Phase behavior of a cell fluid model with modified Morse potential.} \textit{Ukr. J. Phys.} \textbf{65}, 428 (2020) [doi: 10.15407/ujpe65.5.428]
	%10
	\bibitem{DKRP24} O.A.~Dobush, M.P.~Kozlovskii, R.V.~Romanik, I.V.~Pylyuk.
	\href{https://doi.org/10.48550/arXiv.2409.09786}{Thermodynamic response functions in a cell fluid model}. \textit{Ukr. J. Phys} - in print [doi: 10.48550/arXiv.2409.09786]
	%11
	\bibitem{DKRP24arxiv} O.A.~Dobush, M.P.~Kozlovskii, R.V.~Romanik, I.V.~Pylyuk.
	\href{https://doi.org/10.48550/arXiv.2409.09786}{Thermodynamic response functions in a cell fluid model}. \textit{arXiv preprint} 2409.09786 (2024) [doi: 10.48550/arXiv.2409.09786]
	%12
	\bibitem{Morse29} P.~M.~Morse. 
	\href{https://link.aps.org/doi/10.1103/PhysRev.34.57}{Diatomic molecules according to the wave mechanics. II. Vibrational levels.} \textit{Phys. Rev.} \textbf{34}, 57 (1929) [doi: 10.1103/PhysRev.34.57]
	%13
	\bibitem{SBGetal10} G.G.~Simeoni, T.~Bryk, F.A.~Gorelli, M.~Krisch, G.~Ruocco, M.~Santoro, T.~Scopigno.
	\href{https://doi.org/10.1038/nphys1683}{ The Widom line as the crossover between liquid-like and gas-like behaviour in supercritical fluids}. \textit{Nature Phys.} \textbf{6} 503 (2010) [doi: 10.1038/nphys1683]
	%14
	\bibitem{KozlovskiiDobush2016} M.~Kozlovskii, O.~Dobush.
	\href{https://doi.org/j.molliq.2015.12.018}{Representation of the grand partition function of the cell model: The state equation in the mean-field approximation.} \textit{J. Mol. Liq.} \textbf{215}, 58 (2016) [doi: j.molliq.2015.12.018]
	%15
	\bibitem{KR09} M.P~Kozlovskii, R.V.~Romanik.
	\href{https://doi.org/10.30970/jps.13.4007}{The equation of state of a three-dimensional {Ising}-like system}. \textit{Journal of Physical Studies} \textbf{13} 4007 (2009) [doi: 10.30970/jps.13.4007]
	%16
	\bibitem{Kulinskii10jcp} V.L.~Kulinskii.
	\href{https://doi.org/10.1063/1.3457943}{Global isomorphism between the {Lennard-Jones} fluids and the {Ising} model}. \textit{J. Chem. Phys.} \textbf{133} 034121 (2010) [doi: 10.1063/1.3457943]
	%17
	\bibitem{BK11} L.A.~Bulavin, V.L.~Kulinskii.
	\href{https://doi.org/10.1021/jp201872f}{Unified Picture for the Classical Laws of {B}atschinski and the Rectilinear Diameter for Molecular Fluids}. \textit{J. Phys. Chem. B} \textbf{115} 6061 (2011) [doi: 10.1021/jp201872f]

@@
